A Gravitationally Lensed Supernova with an Observable Two-Decade Time Delay

### 2020-06-22 Paper/Science/main.tex
Updates from Overleaf

%BibTeX users: After compilation, comment out the following two lines and paste in
% the generated .bbl file. 
\clearpage
\begin{figure*}
    \centering
    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
    \caption{Overview of the MACSJ0138 cluster field and the locations of the SN Requiem (SN1--3) images and its multiply-imaged host galaxy (H1--4). The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.  Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.  The three-color images are generated from the WFC3/IR filters as indicated; panels $b$--$d$ show the imaging from July 2016 where the SN was visible and $e$--$g$ show the later imaging from July 2019 where the the SN has faded away.  All panels use the late-epoch F125W imaging for the green channel.  Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use to constrain the transient classification as a likely Ia supernova explosion and to constrain the relative age of each SN image.}

@@

\midrule
\textit{1}  & $112^{+20}_{-38}$ & -- & $3.9\pm0.5$ & --\\
\textit{2} & $-27^{+26}_{-6}$ & $139^{+63}_{-23}$ & $7\pm3$ & 101\pm62 \\
\textit{3} & $88\pm15$ & $16\pm19$ & $5\pm1$ & 19\pm34 \\
\textit{4} & -- & -- & $0.4\pm0.2$ & 7761\pm541\\

@@

\begin{table}[]
    \centering
    \begin{tabular}{c|c|c|c|c|c|c|c|}
    Potential & $\Delta$R.A. & $\Delta$Dec. & $e$ & $\theta$ & $\sigma$ & $r_{\rm core}$ & $r_{\rm cut}$ \\
    & [2000.0] & [2000.0] & & [deg] & [km\ $s^{-1}$] & [kpc] & [kpc] \\
\hline
Cluster-DM & $ -0.7^{+  0.4}_{ -0.4}$ & $ -1.2^{+  0.4}_{ -0.4}$ & $ 0.81^{+ 0.02}_{-0.13}$ & $114.9^{+  2.0}_{ -4.1}$ & $31^{+13}_{-12}$ & $[1000]$ & $446^{+52}_{-70}$ \\
BCG & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $[0.15]$ & $136^{+42}_{-32}$ & $700^{+52}_{-57}$ \\
P1 & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[0.15]$ & $[25]$ & $152^{+30}_{-57}$ \\
P2 & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[0.15]$ & $[12]$ & $23^{+111}_{-29}$ \\
P3 & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[0.15]$ & $[6]$ & $110^{+35}_{-32}$ \\
L$^{*}$ galaxy &  & & & & $[0.15]$ & $[45]$ & $[158]$\\
\hline
    \end{tabular}
    \caption{Best fit model parameters for the mass distribution. From left to right: mass component, dPIE center and global shape (ellipticity and orientation), velocity dispersion, core and cut radius. The final row 
    is the generic galaxy mass at the characteristic luminosity L$^*$, which is scaled to match each of cluster member galaxies.  Parameters in square brackets are fixed {\it a priori} in the final model (version E). }
    }
    \label{tab:massmodel}
\end{table}

>>>>

%BibTeX users: After compilation, comment out the following two lines and paste in
% the generated .bbl file. 
\clearpage
\begin{figure*}
    \centering
    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
    \caption{Overview of the MACSJ0138 cluster field and the locations of the SN Requiem (SN1--3) images and its multiply-imaged host galaxy (H1--4). The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.  Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.  The three-color images are generated from the WFC3/IR filters as indicated; panels $bcd$ show the imaging from July 2016 where the SN was visible and $efg$ show the later imaging from July 2019 where the the SN has faded away.  All panels use the late-epoch F125W imaging for the green channel.  Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use to constrain the transient classification as a likely Ia supernova explosion and to constrain the relative age of each SN image.}

@@

\midrule
\textit{1}  & $112^{+20}_{-38}$ & -- & $3.9\pm0.5$ & --\\
\textit{2} & $-27^{+26}_{-6}$ & $139^{+63}_{-23}$ & $7\pm3$ & $101\pm62$ \\
\textit{3} & $88\pm15$ & $16\pm19$ & $5\pm1$ & $19\pm34$ \\
\textit{4} & -- & -- & $0.4\pm0.2$ & $7761\pm541$\\

@@

\begin{table}[]
    \centering
    \begin{tabular}{c|c|c|c|c|c|c|c|}
    Potential & $\Delta$R.A. & $\Delta$Dec. & $e$ & $\theta$ & $\sigma$ & $r_{\rm core}$ & $r_{\rm cut}$ \\
    & [2000.0] & [2000.0] & & [deg] & [km\ $s^{-1}$] & [kpc] & [kpc] \\
\hline
Cluster-DM & $ -0.7^{+  0.4}_{ -0.4}$ & $ -1.2^{+  0.4}_{ -0.4}$ & $ 0.81^{+ 0.02}_{-0.13}$ & $114.9^{+  2.0}_{ -4.1}$ & $31^{+13}_{-12}$ & $[1000]$ & $446^{+52}_{-70}$ \\
BCG            & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $136^{+42}_{-32}$ & $[0.15]$ & $700^{+52}_{-57}$ \\
P1             & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[25]$            & $[0.15]$ & $152^{+30}_{-57}$ \\
P2             & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[12]$            & $[0.15]$ & $23^{+111}_{-29}$ \\
P3             & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[6]$             & $[0.15]$ & $110^{+35}_{-32}$ \\
L$^{*}$ galaxy &           &           &          &           & $[45]$            & $[0.15]$ & $[158]$\\            
%BCG & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $[0.15]$ & $136^{+42}_{-32}$ & $700^{+52}_{-57}$ \\
%P1 & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[0.15]$ & $[25]$ & $152^{+30}_{-57}$ \\
%P2 & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[0.15]$ & $[12]$ & $23^{+111}_{-29}$ \\
%P3 & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[0.15]$ & $[6]$ & $110^{+35}_{-32}$ \\
%L$^{*}$ galaxy &  & & & & $[0.15]$ & $[45]$ & $[158]$\\
\hline
    \end{tabular}
    \caption{Best fit model parameters for the mass distribution. From left to right: mass component, dPIE center and global shape (ellipticity and orientation), velocity dispersion, core and cut radius. The final row 
    is the generic galaxy mass at the characteristic luminosity L$^*$, which is scaled to match each of cluster member galaxies.  Parameters in square brackets are fixed {\it a priori} in the final model (version E). }
    }
    \label{tab:massmodel}
\end{table}
